### 2016-08-11 ms/ms.tex
finished writing results and methods

\begin{abstract}
  TO BE RE-WRITTEN
  The structure of networks is related to ability of communities to
  maintain function in the face of species extinction. Understanding
  network structure and how it relates to network disassembly,
  therefore, is a priority for system-level conservation biology.  We
  explore the assembly of plant-pollinator communities on native plant
  restorations in the Central Valley of California. The assembling
  communities are paired with unrestored field margins (controls) and
  mature (non-assembling) hedgerows. We determine whether there are
  change points in the assembly of the communities where the network
  undergoes significant reorganization. We are also ask how are the
  individual species changing their interaction patterns? What does
  this mean for the topology/resilience of the network? We also
  attempted to adapt a financial model to mutualistic networks. Our
  biggest difficulty with this approach was to translate the price
  term to mutualistic systems. We explored a range of approaches, such
  as number of visits a species performs. However, it seems that
  financial systems cannot be easily translated to mutualistic
  systems. In addition, we used a Changing Point Detection Algorithm
  to assess weather the different communities went through a critical
  reorganization on their interaction patterns. We were able to
  identify some changing points in the communities, and also to
  explore some general patterns commonly used to describe ecological
  networks. For example, on the network level, networks become
  increasingly modular and less nested, whereas on the species level,
  species become more specialized, as resources become more reliable.
\end{abstract}

@@

We calculate species persistence as the proportion of the surveys a
pollinator was observed. Species observed consistently within and
between years are thus maximally persistent. Weighted species degree
is calculated from interaction observations observed in more extensive
data-set from Yolo County (approx.~ 18000 interaction records) that
included both the data included in this study and additional data from
sites where we collected flower visitors using the same methods
\citep{mgonigle-2015-x, ponisio2015farm}.%% does this make sense to
%% calculate from an independent data set?
To represent the the variability of species within networks, we
computed the coefficient of variation of weighted closeness at each
site through time. Closeness describes the centrality of a species in
the network by calculating path lengths to other vertices (species) in
the graph. We used linear mixed models to test whether the variability
of species closeness values was related to the persistence or degree
of that species \citep{lme4, lmetest}. We included random effects for
species, as well as site. We focused on the pollinator species because
the hedgerow flowers are planted and thus are not directly
assembling. Because degree and persistence were strongly correlated,
($\rho = 0.84$, $p$-value $<$ $2*10^{-16}$), each explanatory variable
was included in the model separately. Because a linear increase in
closeness, as might be expected with assembly by preferential
attachment, would lead to a high variability in closeness scores, we
also test whether closeness increases through time.

@@

All five of the assembling hedgerows experienced changing points,
whereas only $40\%$ and $81\%$ of non-assembling hedgerows and field
margins, respectively, underwent significant interaction
reorganizations. Assembling hedgerows experienced significantly more
changing points than the non-assembling networks (difference in the
odds ratios between assembling and non-assembling networks $\pm$
$95\%$ CI, $3.316 \pm 1.314 8.572$, $p$-value= $0.0117$). Network
assembly following restoration is thus punctuated by more interaction
reorganizations than would be expected by environmental shifts that
would effect assembling and non-assembling networks equally.

>>>>

\begin{abstract}
  TO BE RE-WRITTEN
  The structure of networks is related to ability of communities to
  maintain function in the face of species extinction. Understanding
  network structure and how it relates to network disassembly,
  therefore, is a priority for system-level conservation biology.  We
  explore the assembly of plant-pollinator communities on native plant
  restorations in the Central Valley of California. 
\end{abstract}

@@

We calculate species persistence as the proportion of the surveys a
pollinator was observed. Species observed consistently within and
between years are thus maximally persistent. Weighted species degree
is calculated from interaction observations observed in more extensive
data-set from Yolo County (approx.~ 18000 interaction records) that
included both the data included in this study and additional data from
sites where we collected flower visitors using the same methods
\citep{mgonigle-2015-x, ponisio2015farm}. %% does this make sense to
%% calculate from an independent data set?
To represent the the variability of species within networks, we
computed the coefficient of variation of weighted closeness at each
site through time. Closeness describes the centrality of a species in
the network by calculating path lengths to other vertices (species) in
the graph. We used linear mixed models to test whether the variability
of species closeness values was related to the persistence or degree
of that species \citep{lme4, lmetest}. We included random effects for
species, as well as site. We focused on the pollinator species because
the hedgerow flowers are planted and thus are not directly
assembling. Because degree and persistence were strongly correlated,
($\rho = 0.84$, $p$-value $<$ $2*10^{-16}$), each explanatory variable
was included in the model separately. Because a linear increase in
closeness, as might be expected with assembly by preferential
attachment, would lead to a high variability in closeness scores, we
also test whether closeness increases through time.

@@

All five of the assembling hedgerows experienced changing points,
whereas only $40\%$ and $81\%$ of non-assembling hedgerows and field
margins, respectively, underwent significant interaction
reorganizations. Assembling hedgerows experienced significantly more
changing points than the non-assembling networks (difference in the
odds ratios between assembling and non-assembling networks, $3.316$,
$95\%$ CI $[1.314, 8.572]$, $p$-value= $0.0117$). Network assembly
following restoration is thus punctuated by more interaction
reorganizations than would be expected by environmental shifts that
would effect assembling and non-assembling networks equally.
